---
title: "Documentation of Preqin Data Preparation"
author: "Christian Tausch"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document:
    number_sections: true
    highlight: tango
---

# Introduction

This document details the data preparation process for the Preqin cash flow data, as implemented in the corresponding R script. The objective is to clean, filter, and transform raw private market cash flow data into a structured format suitable for empirical asset pricing analysis. The procedure involves data loading, cleaning, calculating incremental cash flows from cumulative reports, and aggregating data into vintage year portfolios.

# Setup and Data Loading

We begin by clearing the workspace and loading necessary libraries. We also define the output directory for the prepared data.

```{r setup, message=FALSE, warning=FALSE}
## prepare preqin
# prep ----
if (sys.nframe() == 0L) rm(list = ls())

library(readxl)
library(here)

data.prepared.folder <- here("empirical/data_prepared_2026")


# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
getwd()
if (!dir.exists(data.prepared.folder)) dir.create(data.prepared.folder)
```

**Note:** The working directory setup line has been commented out to ensure compatibility with R Markdown compilation.

## Loading Raw Data

The raw data is imported from an Excel spreadsheet. The script defines paths for the source file and handles potential inconsistencies in column naming (specifically regarding geographic focus).

```{r load_data}
path <- "empirical/data_in/Preqin_Cashflow_export-26_Feb_20e003d5aa-5a18-4c12-aba8-7586a7435ac9.xlsx"
path <- "empirical/data_in/Preqin_Cashflow_export-14_Apr_22272f54e5-79fe-43c0-8bc0-9206381de0b7.xlsx"
path <- here(path)
sheet <- "Preqin_Export"
df.xl <- data.frame(readxl::read_excel(path = path, sheet = sheet, guess_max = 100000))
if ("GEOGRAPHIC.FOCUS" %in% colnames(df.xl)) df.xl$PRIMARY.GEOGRAPHIC.FOCUS <- df.xl$GEOGRAPHIC.FOCUS
table(df.xl$PRIMARY.GEOGRAPHIC.FOCUS)
colnames(df.xl)

# Exclude too recent vintages
preqin.cutoff.vintage <- 2019
df.xl <- df.xl[df.xl$VINTAGE...INCEPTION.YEAR <= preqin.cutoff.vintage, ]

# df <- df.xl
table(df.xl$ASSET.CLASS[!duplicated(df.xl$FUND.ID)])
table(df.xl$STRATEGY[!duplicated(df.xl$FUND.ID)])
table(df.xl$VINTAGE...INCEPTION.YEAR[!duplicated(df.xl$FUND.ID)])
```

The tables above provide an initial overview of the dataset composition across asset classes, strategies, and vintage years.

# Descriptive Statistics

## Strategy Summary

The `make.strategy.summary` function generates a summary table of the number of funds per strategy within each asset class. This helps in understanding the coverage of the dataset.

```{r strategy_summary}
make.strategy.summary <- function() {
    l <- list()
    for (asset.class in levels(as.factor(df.xl$ASSET.CLASS))) {
        # print(asset.class)
        # print(table(df.xl$STRATEGY[df.xl$ASSET.CLASS == asset.class]))
        df <- data.frame(table(df.xl$STRATEGY[(df.xl$ASSET.CLASS == asset.class) & (!duplicated(df.xl$FUND.ID))]))
        colnames(df) <- c("Strategy", "Fund Count")
        df["Asset Class"] <- asset.class
        df <- df[, c(3, 1, 2)]
        l[[asset.class]] <- df
    }
    df <- data.frame(do.call(rbind, l))

    print(
        xtable::xtable(df,
            caption = "Summary of asset classes in Preqin dataset.",
            digits = 3, label = "tab:summary_preqin_strategy"
        ),
        include.rownames = FALSE
        # , format.args = list(big.mark = ",")
    )
    return(df)
}
make.strategy.summary()
```

## Vintage Year Summary

The `make.vintage.summary` function analyzes the temporal distribution of the funds for a specific asset class (defaulting to Private Equity). It reports the number of distinct funds and separation across vintage years and regions.

```{r vintage_summary}
make.vintage.summary <- function(asset.class = "Private Equity") {
    df <- df.xl[df.xl$ASSET.CLASS == asset.class, ]
    df <- df[!duplicated(df$FUND.ID), ]

    # Create the frequency table
    tbl <- table(df$VINTAGE...INCEPTION.YEAR)

    # Convert table to the desired string format: "Year (Count)"
    # names(tbl) gets the years, and tbl itself contains the counts
    output_string <- paste(paste0(names(tbl), " (", tbl, ")"), collapse = ", ")

    msg <- paste0(
        "The ", asset.class, " sample contains ", length(unique(df$FUND.ID)),
        " distinct funds spreading over ", length(tbl), " vintage years."
    )
    # cat(paste(strwrap(msg, width = 80), collapse = "\n"), "\n\n")
    print(msg)
    
    msg <- paste0("The vintage year distribution is as follows: ", output_string, ".")
    # cat(paste(strwrap(msg, width = 80), collapse = "\n"), "\n")
    print(msg)
    
    # Region split
    tbl <- table(df$REGION)
    output_string <- paste(paste0(names(tbl), " (", tbl, ")"), collapse = ", ")
    msg <- paste0("The region distribution is as follows: ", output_string, ".")
    # cat(paste(strwrap(msg, width = 80), collapse = "\n"), "\n")
    print(msg)
    
    # Strategy split (sub-strategy of the asst class)
    tbl <- table(df$STRATEGY)
    output_string <- paste(paste0(names(tbl), " (", tbl, ")"), collapse = ", ")
    msg <- paste0("The strategy distribution is as follows: ", output_string, ".")
    # cat(paste(strwrap(msg, width = 80), collapse = "\n"), "\n")
    print(msg)
}
make.vintage.summary("Private Equity")
```

# Core Methodology: Cash Flow Construction

The `make.preqin.df` function embodies the core logic for filtering the raw data and constructing the cash flow time series.

**Key Steps:**
1.  **Filtering**: Selects data based on Asset Class (`acs.filter`) and Region (`region.filter`).
2.  **Imputation**: Missing fund sizes are imputed with the mean fund size of the sample.
3.  **Cash Flow Calculation**: The raw data provides cumulative contributions and distributions. We calculate incremental net cash flows (`CF`), contributions (`CON`), and distributions (`DIS`) by taking the first difference of the cumulative series for each fund.
4.  **Terminal Value**: The final Net Asset Value (NAV) reported is treated as a final distribution.
5.  **Data Quality Control**: Funds with less than 2 years of history are excluded.
6.  **Scaling**: All financial values are scaled. If `fund.size.weighting` is TRUE, values are multiplied by the fund size (effectively creating a value-weighted index). Finally, all values are divided by 10 million.
7.  **Aggregation (Optional)**: If `vin.year.pfs` is TRUE, the function aggregates individual fund cash flows into Vintage Year Portfolios (VYP) by averaging metadata-matched cash flows.

```{r core_methodology}
make.preqin.df <- function(
    df = df.xl,
    fund.size.weighting = TRUE,
    acs.filter = "Fund of Funds",
    out.name = "FOF",
    region.filter = NA,
    vin.year.pfs = FALSE) {
    col.to.keep <- c(
        "FUND.ID", "FUND.SIZE..USD.MN.", "VINTAGE...INCEPTION.YEAR",
        "TRANSACTION.DATE", "TRANSACTION.AMOUNT", "NET.CASHFLOW",
        "CUMULATIVE.CONTRIBUTION", "CUMULATIVE.DISTRIBUTION"
    )

    df <- df[df$TRANSACTION.TYPE == "Value", ]

    if (length(acs.filter) > 0) {
        test <- df[df$ASSET.CLASS %in% acs.filter, ]
        if (nrow(test) > 0) df <- test

        test <- df[df$STRATEGY %in% acs.filter, ]
        if (nrow(test) > 0) df <- test
    }

    if (!is.na(region.filter)) {
        df <- df[df$PRIMARY.GEOGRAPHIC.FOCUS %in% region.filter, ]
    }

    df <- df[, col.to.keep]

    for (col in c("FUND.ID")) {
        df[, col] <- as.factor(df[, col])
    }
    df$FUND.SIZE..USD.MN. <- ifelse(is.na(df$FUND.SIZE..USD.MN.),
        mean(df$FUND.SIZE..USD.MN., na.rm = TRUE),
        df$FUND.SIZE..USD.MN.
    )
    df <- df[order(df$FUND.ID, df$TRANSACTION.DATE), ]

    list.df <- list()
    for (fund.id in levels(df$FUND.ID)) {
        df.ss <- df[df$FUND.ID == fund.id, ]
        df.ss <- df.ss[order(df.ss$TRANSACTION.DATE), ]
        df.ss$CF <- c(df.ss$NET.CASHFLOW[1], diff(df.ss$NET.CASHFLOW))
        df.ss$CUMULATIVE.CONTRIBUTION <- c(df.ss$CUMULATIVE.CONTRIBUTION[1], diff(df.ss$CUMULATIVE.CONTRIBUTION))
        df.ss$CUMULATIVE.DISTRIBUTION <- c(df.ss$CUMULATIVE.DISTRIBUTION[1], diff(df.ss$CUMULATIVE.DISTRIBUTION))
        # for last date: CF = CF + NAV, i.e., regard final NAV as final distribution
        final.nav <- df.ss$TRANSACTION.AMOUNT[nrow(df.ss)]
        df.ss$CF[nrow(df.ss)] <- df.ss$CF[nrow(df.ss)] + final.nav

        year.diff <- min(as.numeric(format(df.ss$TRANSACTION.DATE, "%Y"))) - as.numeric(df.ss$VINTAGE...INCEPTION.YEAR[1])
        
        if (is.na(final.nav)) print(paste("Missing Final NAV:", fund.id))
        
        if ((abs(year.diff) < 2) & (!is.na(final.nav))) {
            list.df[[fund.id]] <- df.ss
        }
    }
    df <- data.frame(do.call(rbind, list.df))

    if (fund.size.weighting) {
        df$CF <- df$CF * df$FUND.SIZE..USD.MN.
        df$TRANSACTION.AMOUNT <- df$TRANSACTION.AMOUNT * df$FUND.SIZE..USD.MN. # aka NAV
        df$CUMULATIVE.CONTRIBUTION <- df$CUMULATIVE.CONTRIBUTION * df$FUND.SIZE..USD.MN.
        df$CUMULATIVE.DISTRIBUTION <- df$CUMULATIVE.DISTRIBUTION * df$FUND.SIZE..USD.MN.
    } else {
        # df$CF <- df$CF * mean(df$FUND.SIZE..USD.MN.) # why?
        df$CF <- df$CF
    }

    ten.mio <- 10 * 1000 * 1000
    df$CF <- df$CF / ten.mio
    df$TRANSACTION.AMOUNT <- df$TRANSACTION.AMOUNT / ten.mio # aka NAV
    df$CUMULATIVE.CONTRIBUTION <- df$CUMULATIVE.CONTRIBUTION / ten.mio
    df$CUMULATIVE.DISTRIBUTION <- df$CUMULATIVE.DISTRIBUTION / ten.mio
    df <- df[, c(
        "FUND.ID", "TRANSACTION.DATE", "CF",
        "TRANSACTION.AMOUNT", "CUMULATIVE.CONTRIBUTION", "CUMULATIVE.DISTRIBUTION",
        "VINTAGE...INCEPTION.YEAR"
    )]
    colnames(df) <- c("Fund.ID", "Date", "CF", "NAV", "CON", "DIS", "Vintage")
    df$type <- out.name

    # Vintage Year Porftolio Formation
    agg.vin.year.pf <- function(df) {
        Vintage <- df$Vintage[1]
        type <- df$type[1]
        df.out <- aggregate(CF ~ Date, data = df, mean)
        df.nav <- aggregate(NAV ~ Date, data = df, mean)
        df.out <- merge(df.out, df.nav, by = "Date")
        df.con <- aggregate(CON ~ Date, data = df, mean)
        df.out <- merge(df.out, df.con, by = "Date")
        df.dis <- aggregate(DIS ~ Date, data = df, mean)
        df.out <- merge(df.out, df.dis, by = "Date")
        df.out$type <- type
        df.out$Vintage <- Vintage
        df.out$Fund.ID <- paste0(Vintage, "_", type)
        df.out <- df.out[order(df.out$Date), ]
        return(df.out)
    }
    if (vin.year.pfs) {
        dfx <- split(df, df$Vintage)
        df <- data.frame(do.call(rbind, lapply(dfx, agg.vin.year.pf)))
    }
  
    return(df)
}
df <- make.preqin.df(acs.filter = "Private Equity")
length(df$Fund.ID[!duplicated(df$Fund.ID)])
```

# Execution and Output

Finally, we define a list of asset classes and their corresponding labels. The `make.preqin.csv` function iterates through these asset classes, applies the cleaning function with specified parameters (weighted/unweighted, VYP/Individual, Region), and saves the results to CSV files.

```{r execution}
# run ----

acs <- list(
    INF = "Infrastructure",
    NATRES = "Natural Resources",
    PD = "Private Debt",
    PE = "Private Equity",
    RE = "Real Estate",
    VC = "Venture Capital",
    MEZZ = "Mezzanine",
    DD = c("Special Situations", "Distressed Debt"),
    BO = "Buyout",
    GroBO = c("Growth", "Buyout"),
    FOF = "Fund of Funds",
    SEC = "Secondaries"
)


make.preqin.csv <- function(fund.size.weighting, vin.year.pfs, region.filter) {
    l <- list()
    for (i in names(acs)) {
        print(acs[[i]])
        df0 <- make.preqin.df(
            fund.size.weighting = fund.size.weighting,
            acs.filter = acs[[i]],
            region.filter = region.filter,
            vin.year.pfs = vin.year.pfs,
            out.name = i
        )
        l[[i]] <- df0
    }
    df.out <- data.frame(do.call(rbind, l))

    tag <- ifelse(fund.size.weighting, "FW", "EW")
    tag <- ifelse(vin.year.pfs, paste0(tag, "_VYP"), tag)
    tag <- ifelse(is.na(region.filter), tag, paste0(tag, "_", region.filter))
    file <- paste0(data.prepared.folder, "/preqin_cashflows_2022_", tag, "_NAV.csv")
    file <- paste0(data.prepared.folder, "/preqin_cashflows_", tag, "_NAV.csv")
    write.csv(df.out, file, row.names = FALSE)
    invisible(df.out)
}
# Execute for various configurations
df.out <- make.preqin.csv(TRUE, TRUE, NA)
df.out <- make.preqin.csv(FALSE, TRUE, NA)
df.out <- make.preqin.csv(TRUE, FALSE, NA)
df.out <- make.preqin.csv(FALSE, FALSE, NA)
df.out <- make.preqin.csv(TRUE, TRUE, "Europe")
df.out <- make.preqin.csv(FALSE, TRUE, "Europe")
```
