\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{hidelinks}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}
\setlist[itemize]{leftmargin=1.3em,itemsep=0.2em,topsep=0.2em}
\setlist[enumerate]{leftmargin=1.5em,itemsep=0.2em,topsep=0.2em}

\newcommand{\tbd}[1]{\textbf{[TBD: #1]}}

\begin{document}

{\Large\bfseries Historical Transportability of Private-Capital SDFs\par}
{\normalsize Which historical cash flows are relevant for pricing current funds?\par}
\today

\begin{abstract}
Private-capital SDF estimation faces a three-way data constraint. There are few
vintage years, older vintages may transport poorly to current funds, and the
most recent vintages have not yet produced the realized cash flows needed for
appraisal-free estimation. We propose a relevance-weighted hybrid estimator
that treats the historical information set itself as a model-selection object.
Seasoned vintages contribute realized-cash-flow NPV moments; unseasoned
vintages can contribute short-horizon NAV Euler errors; and historical
vintages are weighted by temporal proximity and similarity in credit spreads,
interest rates, and public-market valuations. Expanding, rolling, decaying,
and state-conditioned SDFs are compared on a common NAV-free criterion. An
ex-post transportability matrix measures how well an SDF estimated in one
historical window prices earlier and later realized vintages. A forward
pseudo-real-time exercise then jointly selects the SDF specification, the
historical weighting scheme, and whether unseasoned Euler moments improve
subsequent realized-cash-flow pricing relative to excluding young funds. The
paper does not claim that thirty vintage years can cleanly distinguish a
stable law from every form of temporal instability. It asks the empirically
sharper question: which use of the available history travels best out of
sample?
\end{abstract}

\section{Introduction}

How much historical private-capital data should be used to estimate an SDF
for a fund raised today? Under a stable and sufficiently mixing data-generating
process, older vintages add information and a full-history estimator becomes
increasingly precise. Under temporal instability, however, the same estimator
may converge precisely to a historical mixture that is no longer the relevant
pricing law for current funds. More funds within a vintage can reveal that
vintage's pricing moment more accurately, but they cannot create additional
independent economic histories.

This creates a three-way empirical constraint. First, the time-series dimension
is intrinsically thin: even a long private-capital database contains only a few
dozen vintage years, and adjacent vintages live through overlapping calendar
histories. Second, increasing the sample by reaching further into the past
requires a transport assumption: that pricing relations estimated on older
funds remain relevant for funds raised under different financing, valuation,
and exit conditions. Third, restricting estimation to fully realized cash
flows removes precisely the recent vintages that are most informative about
the current environment. Conventional resampling can reduce fund noise inside
the observed sample, but it cannot create economic time or resolve this
maturity delay.

The private-equity pricing literature has developed several ways to recover
risk and performance from irregular, non-traded cash flows.
\citet{DriessenLinPhalippou2012} estimate factor exposures and abnormal
performance directly from fund cash flows --- the discounting framework our
estimator adopts throughout --- while
\citet{AngChenGoetzmannPhalippou2018} recover a time series of private-equity
returns from limited-partner cash flows. \citet{KortewegNagel2016} use a
generalized public-market-equivalent approach to risk-adjust venture-capital
cash flows. More recent work refines cash-flow benchmarking and SDF-based
performance measurement \citep{GredilGriffithsStucke2023,KortewegNagel2025}.
These approaches differ in their maintained pricing restrictions and treatment
of illiquidity, but they largely take the historical estimation sample as
given. Our paper instead asks which part of that sample is informative for a
current pricing problem: how well does an estimated private-capital SDF
transport across economic time?

We call the empirical ability of an SDF estimated in one historical window to
price cash flows from another window \emph{historical transportability}. A
stable pricing relation should travel across windows; a temporally unstable
one should exhibit loss that changes with the distance and economic difference
between estimation and evaluation periods. The concept does not require a
literal regime classification. Smooth drift, isolated breaks, changes in the
support of economic states, and changes in fund composition can all appear as
failures of transportability. In an environment this short, a global test of
``stability versus instability'' is unlikely to have useful power against the
many plausible alternatives. We therefore follow the forecasting-under-
instability logic of evaluating local predictive performance rather than
making a structural-break test the paper's central result
\citep{PesaranTimmermann2007,Rossi2021}.

Our proposed solution is a \emph{forward-selected relevance-weighted hybrid
SDF}. It has three components. First, candidate SDFs are estimated under a
small, pre-specified sequence of historical weighting schemes: the full
expanding sample, hard rolling windows, exponential time decay, and a
time-and-state kernel. Second, recent economic similarity is measured with
three observable state variables fixed before evaluating fund performance:
credit spreads, the interest-rate level, and public-market valuations. Third,
recent unseasoned vintages enter through short-horizon NAV Euler restrictions,
but their inclusion is not maintained by assumption: the hybrid estimator is
compared with an otherwise identical estimator that excludes them. Every
choice is judged on later realized cash flows.

The empirical design has two parts. An ex-post transportability matrix uses
fully realized vintages to show how pricing laws travel forward and backward
across historical windows. Its backward entries are structural diagnostics,
not feasible forecasts. A pseudo-real-time exercise then recreates historical
information dates, estimates each candidate using the information available
at that origin, and scores it on cash flows realized later by the then-young
funds. This second exercise provides the directional evidence required to
choose a current estimator.

The paper makes four contributions.
\begin{enumerate}
\item It formulates the private-capital data problem as a joint constraint of
      few economic histories, potentially decaying historical relevance, and
      delayed cash-flow outcomes.
\item It introduces historical transportability matrices and signed-distance
      loss curves that show where and how far a private-capital SDF travels.
\item It proposes a relevance-weighted SDF that combines simple temporal
      windows with low-dimensional economic-state similarity, while enforcing
      an effective-sample-size and identification constraint.
\item It evaluates the informational value of unseasoned NAV Euler moments on
      a common, later-realized cash-flow target rather than on NAV fit.
\end{enumerate}

\section{Methodology}

\subsection{The Private-Capital Data Trilemma}

The constraint introduced above has three connected parts: \emph{few
vintages}, because a few dozen vintage years with overlapping fund lives carry
an effective temporal dimension smaller than the vintage count;
\emph{historical relevance}, because adding older vintages reduces sampling
variance only if their pricing relations transport to the target period ---
under instability a precisely estimated full-history SDF can be precisely
wrong for a current fund; and \emph{delayed outcomes}, because the newest
vintages contain the most current economic information but have not yet
revealed their realized cash flows.

These are not three independent nuisances. Shortening the estimation window
raises temporal relevance but increases sampling uncertainty and concentrates
the sample in unseasoned funds. Requiring realized cash flows pushes the
effective window backward. Reaching further into history restores moment count
at the cost of a stronger transport assumption. The empirical objective is
therefore not to eliminate any one component in isolation, but to find the
combination that produces the lowest forward realized-cash-flow loss.

\subsubsection{What the data can and cannot establish}

Thirty vintage years do not support a clean omnibus decision between a
time-invariant SDF and every form of temporal instability: a failure to reject
stability may reflect low power, and a local episode of poor performance need
not identify a permanent break. The paper therefore reports economically
interpretable loss differences, transport curves, and model sets across a
small pre-specified design space, treating local forecast performance as the
target and parameter instability as one possible explanation for its variation
\citep{Rossi2021}.

\subsubsection{The cost of ignoring recent vintages}

Discarding unseasoned vintages is clean only in a narrow measurement sense. It
also changes the estimand by restricting the current SDF to funds raised far
enough in the past to have substantially realized. Because buyout persistence
and the composition of the industry have changed over time, this restriction
cannot automatically be treated as innocuous \citep{HarrisJenkinsonKaplanStucke2023}.
The exclusion estimator is therefore an essential benchmark, not the default
solution. Whether short-horizon Euler information improves forward pricing is
an empirical question.

\subsection{Pricing Moments}
\label{sec:moments}

A candidate SDF specification $M$ fixes a parametric family of one-period
realizations $M_{t-1,t}(\theta)$ with $\theta\in\Theta_M$; dependence on $M$
is left implicit whenever it is clear from context. Every specification in
this paper belongs to the benchmark-discounting family of
\citet{DriessenLinPhalippou2012}: the one-period discount factor is the
inverse gross return of a levered public benchmark,
\[
M_{t-1,t}(\beta)
=
\frac{1}{1+r_{f,t}+\beta\,(R_{m,t}-r_{f,t})},
\]
so that $\theta=\beta$, with the multifactor case replacing the single excess
return by a vector of factor excess returns. Setting $\beta=0$ prices the
risk-free asset and $\beta=1$ a self-financing public-market investment
exactly, period by period: benchmark pricing is built into the functional
form rather than imposed through auxiliary moments, and no separate
price-of-risk parameter exists. The abnormal-return intercept of the
original method is fixed at zero; Section~\ref{sec:pricinglaw} states the
resulting estimand.\footnote{$\Theta_M$ bounds $\beta$ so that the levered
benchmark return exceeds $-100\%$ in every sample quarter, keeping all
discount factors positive.} Let
$\Psi_{0,t}(\theta)=\prod_{s=1}^{t}M_{s-1,s}(\theta)$ denote the realized
discount factor from fund inception to quarter $t$, with $\Psi_{0,0}=1$, so
that the time-zero capital call enters undiscounted by construction.

\subsubsection{Seasoned vintages}

For seasoned fund $i$ of vintage $v$ with committed capital $K_i$, net dated
cash flows $CF_{t,i}$ (calls negative, distributions positive), and last
observed cash flow at $T_i$, the realized pricing error per committed dollar
is
\[
g_i^S(\theta)
=
\frac{1}{K_i}\sum_{t=0}^{T_i}\Psi_{0,t}(\theta)\,CF_{t,i},
\]
and the seasoned vintage moment is the equal-weighted fund mean
$\epsilon_v^S(\theta)=N_v^{-1}\sum_{i\in v}g_i^S(\theta)$, where $N_v$ is the
number of admissible funds in vintage $v$; commitment-weighted vintage means
are a pre-specified robustness variant.

The same object defines the paper's common evaluation currency. The realized
evaluation loss of a parameter $\theta$ on a seasoned vintage $v$ is
\[
\widehat U_v^{\mathrm{real}}(\theta)=\epsilon_v^S(\theta)^2,
\]
the squared vintage-mean realized pricing error. Squaring the vintage mean,
rather than averaging squared fund-level errors, targets systematic
mispricing and prevents idiosyncratic fund noise --- which no SDF can price
--- from dominating design comparisons; absolute rather than squared vintage
errors are a robustness check. Because $\Psi_{0,t}$ compounds many quarterly
SDF realizations, a small number of extreme discount-factor paths can
dominate both estimation and evaluation. We therefore report the
concentration of loss contributions across vintages and a winsorized-loss
robustness variant.

\subsubsection{Unseasoned vintages}

For an unseasoned fund, the full NPV moment is unavailable without valuing the
residual claim. The baseline bridge uses the short-horizon NAV Euler error
\[
e^H_{t,i}(\theta)
=
M_{t-1,t}(\theta)R^H_{t,i}-1,
\]
where $R^H_{t,i}$ is the quarterly Horizon-IRR return accounting for interim
calls and distributions. The unseasoned vintage moment scales the pooled
fund-quarter mean into the units of the seasoned block:
\[
\epsilon_v^U(\theta)
=
\bar D\cdot
\frac{1}{n_v^U}\sum_{(i,t)\in v}e^H_{t,i}(\theta),
\]
where $n_v^U$ is the number of admissible fund-quarters of vintage $v$ and
$\bar D$ is the median discounted duration, in quarters, of seasoned funds in
the estimation sample, fixed before any out-of-sample comparison. The scaling
has a first-order justification: a pricing error of $e$ per quarter sustained
over a fund's life accumulates to a lifetime NPV error of approximately
duration times $e$, so both blocks are expressed in NPV per committed dollar
and can legitimately share one set of relevance weights. Euler errors are
never discounted back to inception and never enter the comparison score.
Reported NAVs are noisy appraisals, so this block is treated
as a candidate information bridge rather than a traded-return restriction that
must hold exactly. State-space corrected NAVs are a robustness extension, not
the baseline \citep{brown2023nowcasting}.

The main unseasoned-treatment comparison is deliberately parsimonious:
\begin{enumerate}
\item \emph{Exclude}: estimate only with seasoned realized-cash-flow moments;
\item \emph{Hybrid}: add short-horizon NAV Euler moments for unseasoned
      vintages.
\end{enumerate}
Both are evaluated on the identical subsequently realized cash flows. A more
complicated measurement model earns a place in the main design only if the
simple comparison demonstrates economically meaningful value from recent NAV
information.

\subsection{The Relevance-Weighted Hybrid SDF}

At target date $T$, let $z_v$ collect the economic state associated with
vintage $v$. The baseline state vector contains three pre-performance
variables: a credit spread, the interest-rate level, and a public-market
valuation ratio. The variables are measured at or immediately before vintage
formation and standardized using the estimation sample only.

For historical vintage $v$, define the unnormalized relevance weight
\[
w_{v,T}(h,b)
=
\exp\!\left[-\log(2)\frac{T-v}{h}\right]
\exp\!\left[-\frac{1}{2b^2}
  (z_v-z_T)'(z_v-z_T)\right],
\]
where $h$ is a time half-life and $b$ is a common state-similarity bandwidth.
The simple common bandwidth avoids estimating three separate state-sensitivity
parameters from a few dozen vintages. Setting $h=\infty$ removes time decay;
setting $b=\infty$ removes state conditioning. Hard rolling windows are
obtained by replacing the time-decay component with an indicator.

Let $q_v$ be a reliability weight, set to the vintage fund count $N_v$ in the
baseline; vintage-equal weighting ($q_v=1$) is a pre-specified robustness
variant. The products $w_{v,T}q_v$ are normalized to sum to one jointly
across all vintages entering the objective, seasoned and unseasoned alike, so
that a vintage's relevance does not depend on the block through which it
enters. For candidate unseasoned treatment
$A\in\{\mathrm{Exclude},\mathrm{Hybrid}\}$, estimate
\[
\widehat\theta_T(M,h,b,A)
=
\arg\min_{\theta\in\Theta_M}
\left\{
\sum_{v\in\mathcal V_T^S}\widetilde w_{v,T}
  \epsilon_v^S(\theta)^2
+
\mathbf 1\{A=\mathrm{Hybrid}\}
\sum_{v\in\mathcal V_T^U}\widetilde w_{v,T}
  \epsilon_v^U(\theta)^2
\right\}.
\]
We collect a complete design in the tuple $c=(M,h,b,A)$ and write
$\widehat\theta_T(c)$ below. Because unseasoned vintages are by construction
the most recent, time decay concentrates weight on the Euler block: under
short half-lives the hybrid objective becomes increasingly NAV-driven. Every
configuration therefore reports its realized unseasoned weight share
$\pi_U(T;h,b)=\sum_{v\in\mathcal V_T^U}\widetilde w_{v,T}$, which makes this
interaction visible rather than leaving it implicit in the kernel.

The design sequence moves from transparent to reasonably sophisticated while
remaining feasible in a thin vintage panel:
\begin{enumerate}
\item \textbf{Expanding}: equal weight on the full available history;
\item \textbf{Rolling}: equal weight inside a fixed recent-vintage window;
\item \textbf{Decay}: exponential time weights indexed by half-life $h$;
\item \textbf{Time--state}: exponential decay combined with similarity in
      credit spreads, interest rates, and public valuations.
\end{enumerate}

A regularized time-varying parameter path of the form
\[
\min_{\{\theta_v\}}
\sum_v\epsilon_v(\theta_v)^2
+\kappa\sum_{v>1}\|\theta_v-\theta_{v-1}\|_2^2
\]
is the principal sophistication check \citep{CuiFengHong2024}. Its
target-date parameter is the final element of the estimated path, and
$\kappa$ is selected on strictly earlier origins under the sequential
protocol of Section~\ref{sec:forward}. It is not the headline estimator
unless it produces a clear forward improvement over the lower-dimensional
weighting schemes.

Every candidate must satisfy two feasibility restrictions before it can be
scored: the weighted moment Jacobian must be sufficiently well conditioned,
and the weight concentration must leave an effective vintage count
\[
V_{\mathrm{eff}}(T)=\frac{1}{\sum_v\widetilde w_{v,T}^2}
\]
comfortably above the number of SDF parameters. The count is computed both
over all vintages and, with weights renormalized within the block, over the
seasoned block alone; the threshold must hold for the seasoned block, since
realized cash flows anchor identification. This prevents an apparently local
estimator from being driven by one historically similar vintage or propped up
by appraisal-based moments alone.

\subsubsection{Pricing law versus performance measurement}
\label{sec:pricinglaw}

The estimator is a pricing-law estimator, not a performance measure. With the
abnormal-return intercept fixed at zero, average in-window performance is
absorbed into the exposure estimate through the premium channel: to first
order the fitted exposure is $\beta^*\approx\beta+\alpha/\lambda$, where
$\alpha$ is average abnormal performance and $\lambda$ the factor premium.
The estimand is therefore the composite pricing-law beta --- the leverage on
the public benchmark that best rationalizes the weighted history --- not a
pure risk exposure. Freeing the intercept would separate the two in
principle, but a per-period intercept compounded over decade-long fund lives
is fragile in a thin vintage panel, and we exclude it by design. Statements
about risk-adjusted performance in this paper therefore refer exclusively to
out-of-window residuals --- realized pricing errors of vintages that did not
enter, or received negligible weight in, the estimation sample. In-window
residuals are diagnostics of fit, never evidence of abnormal performance.
Section~\ref{sec:transportmeaning} turns this absorption into a testable
implication for out-of-window residuals.

\subsection{Historical Transportability}

\subsubsection{The transportability matrix}

Let $s$ index a historical estimation window and $t$ an excluded, fully
realized evaluation vintage. Throughout this subsection $s$ denotes the
window's information end date; where present, the time-decay and state
kernels are centered on $s$ and $z_s$, and $A=\mathrm{Exclude}$ is imposed.
Define the NAV-free transport loss
\[
L_{s\rightarrow t}(c)
=
\widehat U_t^{\mathrm{real}}\!\left(
  \widehat\theta_s(c)
\right),
\]
where the evaluation score uses only realized fund cash flows. The exclusion
version isolates historical transportability from the separate question of
how young-fund NAV information enters. Stacking these losses over estimation
windows and evaluation vintages yields a
\emph{historical transportability matrix}. Its rows are window SDFs, its
columns are evaluation vintages, and each entry measures how well a pricing
law travels across economic time.

Aggregating by the signed temporal distance $d=t-s$, measured from the window
end, gives the transport loss curve
\[
\mathcal T_c(d)
=
\frac{1}{N_d}\sum_s L_{s\rightarrow s+d}(c).
\]
Positive distances measure forward transportability; negative distances
measure backward transportability. Only the former has a real-time forecasting
interpretation. Backward transportability is a diagnostic of structural
stability, not a feasible investment rule.

The matrix is descriptive by design. A flat surface is consistent with broad
historical transportability; loss increasing in $|d|$ is consistent with
temporal localization; and isolated high-loss columns indicate historically
unusual target periods. None of these patterns alone proves a particular
structural-break model.

\subsubsection{Calendar-time overlap}

Adjacent vintage moments share public-factor histories because their funds
remain active for many years. We therefore measure pairwise calendar-time
overlap rather than treating vintage labels as independent by construction.
Let $a_{v,t}$ denote vintage $v$'s absolute discounted cash-flow exposure to
calendar period $t$, evaluated at reference parameter values fixed in
advance.\footnote{A Jacobian-based exposure measure yields an alternative
overlap matrix and is reported as a variant.} Define
\[
O_{vv'}
=
\frac{\sum_t a_{v,t}a_{v',t}}
{\sqrt{\sum_ta_{v,t}^2}\sqrt{\sum_ta_{v',t}^2}}.
\]
The overlap matrix is reported alongside the transportability matrix.
Estimation--evaluation pairs with overlap above a pre-specified threshold are
flagged, and headline comparisons are re-reported excluding them. Because
complete separation would eliminate most of the data, overlap is quantified
and stress-tested rather than treated as a binary admissibility standard.

\subsubsection{Absorbed premia, omitted factors, and the meaning of transport loss}
\label{sec:transportmeaning}

The premium channel of Section~\ref{sec:pricinglaw} has a testable
implication. Let $\widehat\lambda_s$ and $\widehat\lambda_t$ denote the
realized benchmark premia over the weighted estimation window and over the
cash-flow-weighted life of evaluation vintage $t$. If true performance is
$(\alpha,\beta)$, estimation forces
$\beta^*=\beta+\alpha/\widehat\lambda_s$, and the signed transport residual
is, to first order and in per-period units,\footnote{NPV residuals per
committed dollar scale with fund duration; dividing by $\bar D$ of
Section~\ref{sec:moments} expresses them in the per-period units used here.}
\[
\epsilon_t^S\!\left(\widehat\theta_s\right)
\;\approx\;
\alpha\left(1-\frac{\widehat\lambda_t}{\widehat\lambda_s}\right),
\]
linear in the realized evaluation premium with intercept $\alpha$ and slope
$-(\beta^*-\beta)$. Under the composite null $\alpha=0$ the line is flat at
zero. Regressing signed transport residuals on realized evaluation premia is
therefore both a specification test of the zero-intercept design and, upon
rejection, a first-order recovery of the split: the intercept estimates
$\alpha$ and $\beta=\beta^*+\text{slope}$. With few effective windows this
\emph{premium-exposure diagnostic} is reported with uncertainty bands, as a
diagnostic rather than a second estimator.

The same channel governs omitted factors. Decompose an omitted factor into
its projection on the included benchmarks and an orthogonal remainder. The
spanned component shifts the included exposures by the usual
omitted-variable term and is harmless for pricing while factor correlations
are stable. The unspanned premium component is observationally identical to
$\alpha$: skill and unspanned factor premia are the same object in cash-flow
data and are absorbed together into $\beta^*$. Three corollaries follow.
\begin{enumerate}
\item \textbf{Constant unspanned premia transport.} A stable absorbed
      component enters $\beta^*$ identically in every window; transport
      residuals remain mean-zero, and only their variance rises with premium
      variability. The composite prices without the true factor model.
\item \textbf{Time-varying unspanned premia are what transport failure
      detects.} A premium that shifts across regimes makes a window-fitted
      $\beta^*$ systematically misprice other windows. Loss rising with
      temporal or state distance therefore has a direct asset-pricing
      reading, and the premium-exposure diagnostic extends to candidate
      premia --- realized credit or illiquidity-proxy returns --- to name
      the missing factor.
\item \textbf{The time--state kernel is the reduced-form hedge.}
      Conditioning estimation windows on credit spreads, rates, and
      valuations estimates the composite locally in states where omitted
      premia are plausibly similar. The kernel does not claim to know the
      missing factors; it conditions on their observable proxies.
\end{enumerate}
The multifactor menu addresses only the spanned component; the unspanned
component is invisible inside any single window and visible only through
transport. This is the information-theoretic limit of cash-flow data, and it
is why the paper selects on forward transport loss rather than on in-window
fit.

\subsection{Unseasoned Vintages as Delayed Outcomes}

At historical information date $\tau$, estimate $\widehat\theta_\tau(c)$ by
minimizing the weighted objective of the previous subsection using only fund
information dated no later than $\tau$. Candidate bridges are compared on the
identical realized-cash-flow target after the then-unseasoned vintages have
seasoned:
\[
L_{\tau\rightarrow\tau+\ell}(c)
=
\frac{1}{|\mathcal V^U_\tau\cap\mathcal V^S_{\tau+\ell}|}
\sum_{v\in\mathcal V^U_\tau\cap\mathcal V^S_{\tau+\ell}}
\widehat U_v^{\mathrm{real}}
\!\left(\widehat\theta_\tau(c)\right).
\]

One convention deserves emphasis. The time and state kernels remain centered
on the origin, $\tau$ and $z_\tau$, while the scored vintages were raised
shortly before $\tau$ under possibly different states. The forward loss
therefore validates the estimator as a pricing rule for recently raised
funds, and its application to a fund raised at the current date extrapolates
the transport pattern by one further step. We state this openly rather than
re-center the kernel on each evaluation vintage, which would replace a single
origin SDF with a vintage-indexed family at substantial computational cost
and little expected gain when origin and formation states are close.

The empirical comparison therefore selects a triplet: the SDF specification,
the historical weighting rule, and the unseasoned-vintage treatment. Exclusion
remains in the race as the benchmark measuring the cost of delayed outcomes;
the short-horizon Euler block is the proposed simple bridge. The paper presents
the configuration with the lowest forward loss as its preferred empirical
solution, subject to the feasibility and stability diagnostics above.

\subsection{Evaluation Design}

\textbf{Ex-post transportability.} Estimate local SDFs on fully observed
historical windows and score them on earlier and later seasoned vintages. This
exercise is fully NAV-free and isolates temporal transportability, but it does
not claim a real-time interpretation when later information is used to estimate
an SDF that is scored on an earlier period.

\textbf{Pseudo-real-time delayed-outcome validation.} Reconstruct a sequence of
historical information dates, estimate each window/bridge combination using
the information fields available at the corresponding date, and score it on
subsequently realized fund cash flows. A literal real-time reconstruction would
also require historical database snapshots, contemporaneous coverage records,
and knowledge of which observations were later backfilled. Imposing that ideal
would leave essentially no usable evaluation sample. We therefore adopt the
pragmatic pseudo-real-time standard feasible in the data and state its residual
look-ahead limitation explicitly.\footnote{The fully reconstructed real-time
ideal is conceptually useful even when empirically infeasible: it identifies
the remaining source of look-ahead without pretending that an empty sample is
a superior research design.}

The design grid is intentionally coarse and common across SDF specifications;
Section~\ref{sec:forward} separates the paired comparison of fixed designs
from the sequential evaluation of the selection rule itself. A further
structural limitation is timing: because a vintage needs roughly a decade to
season, the last scoreable origin precedes the end of the sample by
approximately one seasoning lag. Statements about funds raised at the current
date therefore extrapolate a selection rule whose direct validation
necessarily ends earlier, and the paper says so rather than implying that
pseudo-real-time evidence reaches the present.

\subsection{Forward Selection Criterion}
\label{sec:forward}

Let $\mathcal O$ denote the admissible pseudo-real-time origins and
$\mathcal H_\tau$ the vintages that were unseasoned at $\tau$ and later become
eligible for realized-cash-flow scoring. For design
$c=(M,h,b,A)$, define
\[
\widehat R(c)
=
\frac{1}{|\mathcal O|}
\sum_{\tau\in\mathcal O}
\frac{1}{|\mathcal H_\tau|}
\sum_{v\in\mathcal H_\tau}
\widehat U_v^{\mathrm{real}}
\!\left(\widehat\theta_\tau(c)\right).
\]
All designs face the same origins and realized evaluation funds, so
comparisons are paired. Two protocols use this criterion for different
purposes.

\textbf{Protocol A: fixed-design comparison (headline).} Every design in the
pre-specified grid is estimated at every admissible origin and scored on the
identical origin--vintage cells. No tuning occurs; the coarse grid is the
pre-registration. The preferred design minimizes $\widehat R(c)$ and is
reported together with the model confidence set of designs whose forward loss
is not significantly worse \citep{HansenLundeNason2011}, so that small
differences are not given a false winner-takes-all interpretation.

\textbf{Protocol B: sequential selection (implementability check).} Because
the Protocol~A minimizer is chosen using all origins, we also evaluate the
selection rule itself: at each origin $\tau$, the design minimizing
$\widehat R$ computed over strictly earlier origins is scored on origin
$\tau$ alone. The average of these sequentially selected losses measures what
forward selection would have delivered in real time. With few origins this
estimate is noisy, and it is reported as a check on Protocol~A rather than as
the headline comparison.

The paper emphasizes effect sizes, origin-by-origin stability, and
sensitivity to the coarse grid. With only a few dozen vintage years, formal
rejections of equal predictive loss are interpreted cautiously.

\subsection{Inference and Reporting}

Model comparisons use paired loss differences because every admissible design
is evaluated on the same origin--vintage cells \citep{GiacominiWhite2006}.
Losses are first averaged within origin so that origins with many funds or
newly seasoned vintages do not dominate mechanically. Because adjacent annual
origins share most of their evaluation vintages, the same realized outcome
enters $\widehat R$ at several origins, and the effective number of
independent evaluations is far smaller than $|\mathcal O|$; the number of
distinct evaluation vintages and funds behind each comparison is therefore
reported alongside the origin-coverage table. We report the mean paired
difference, its distribution across origins, and block-bootstrap uncertainty
that preserves adjacent-origin dependence. The premium-exposure diagnostic of
Section~\ref{sec:transportmeaning} is reported alongside these comparisons. Parameter uncertainty for a selected SDF is assessed with vintage-
level resampling and calendar-overlap blocks. Given the short time series and
the additional uncertainty created by model selection, confidence intervals
and predictive-loss tests are interpreted as measures of precision rather than
as a binary stability verdict.

\section{Data and Empirical Design}

This section maps the empirical inputs directly into the moments, state
weights, and forward loss defined above. The ordering is deliberate: we first
construct an appraisal-free realized-cash-flow target, then define what was
observable at each historical origin, and only then compare alternative uses of
the available history.

\subsection{Private-Capital Cash-Flow Data}

The fund data are drawn from \tbd{data provider and extraction date}. The unit
of observation is a dated limited-partner cash flow for a \tbd{buyout / broader
private-capital} fund. Required fields are fund identifier, vintage year,
commitment, dated capital calls, dated distributions, reported NAVs, strategy,
geography, and --- where available --- general-partner identifier. Cash flows
and NAVs are measured net of management fees and carried interest from the
limited partner's perspective and converted to \tbd{currency and real/nominal
units}. We exclude funds with internally inconsistent cash-flow histories,
missing commitments, nonpositive commitments, or implausible scale ratios
under a pre-specified cleaning rule. The analysis retains all admissible funds
within a vintage; it does not create pseudo-vintages by resampling funds.

The first data table should make the thin time-series dimension visible rather
than reporting only a large fund count:

\begin{table}[htbp]
\centering
\caption{Private-capital sample by vintage period}
\label{tab:sample}
\small
\begin{tabular}{lrrrrr}
\toprule
Vintage period & Vintages & Funds & Commitments & Funds/vintage & Realized share \\
\midrule
\tbd{early period}  & & & & & \\
\tbd{middle period} & & & & & \\
\tbd{recent period} & & & & & \\
\midrule
Full sample & & & & & \\
\bottomrule
\end{tabular}
\begin{minipage}{0.94\textwidth}
\footnotesize \emph{Notes:} Commitments are reported in \tbd{units}. Funds per
vintage is the median across vintage years. Realized share is the fraction of
funds satisfying the baseline seasoning rule at the final sample date.
\end{minipage}
\end{table}

\subsection{Seasoning and the Realized Evaluation Sample}

At information date $\tau$, a fund is seasoned when its residual value share
\[
s_{i,\tau}
=
\frac{\mathrm{RVPI}_{i,\tau}}
{\mathrm{DPI}_{i,\tau}+\mathrm{RVPI}_{i,\tau}}
\]
is at most $\delta$. The proposed baseline is $\delta=0.15$, with $0.10$ and
$0.20$ as pre-specified robustness thresholds. A fund that fails this rule may
contribute to the hybrid short-horizon Euler block but never to the realized
evaluation loss at that date. The realized target includes only calls and
distributions observed by the evaluation date; the residual NAV is used to
determine eligibility but is neither priced nor added as a terminal cash flow.
Thus, $\delta$ trades bounded terminal truncation for sample size without
fitting the score to NAV; $\delta=0$ is the strict robustness check.

We report, for every pseudo-real-time origin, the number of available vintages,
seasoned and unseasoned funds, the fraction of commitment represented by the
realized evaluation set, and the later vintages that can eventually be scored.
This origin-by-origin coverage table is essential: it reveals whether an
apparent forecasting gain comes from a genuinely broader information set or
from a small and unusual set of funds that happens to mature early.

\subsection{Public Factors and Candidate SDFs}

Public-market returns and the risk-free rate are obtained from \tbd{source} at
the same frequency as the cash-flow discounting exercise. All candidate SDFs
are members of the single benchmark-discounting family of
Section~\ref{sec:moments}, and the main comparison uses a deliberately small
nested set: $\beta=0$ (risk-free discounting), $\beta=1$ (the
public-market-equivalent benchmark), a freely estimated one-factor $\beta$,
and a freely estimated low-dimensional multifactor $\beta$ vector. This keeps
the empirical question focused on the historical information set rather than
on kernel functional forms or a factor zoo. Factor definitions, currency,
return convention, and the mapping from quarterly factors to dated cash flows
are fixed before inspecting forward pricing losses.

\subsection{Economic-State Variables}

The state vector $z_v$ contains one variable for each of three economic
dimensions: a corporate credit spread, the interest-rate level, and a public-
equity valuation ratio. The proposed baseline definitions are the high-yield
option-adjusted spread, a long-term nominal government yield, and the cyclically
adjusted price--earnings ratio \tbd{or a price--dividend ratio}. To avoid using
fund outcomes to define similarity, each variable is measured as its average
over the 12 months ending immediately before the vintage year. At each origin,
levels are standardized using only the available estimation vintages. We also
report the historical support of $z_T$; a target outside that support is an
extrapolation problem and should not receive a falsely precise local estimate.

\subsection{Pseudo-Real-Time Origins}

Annual origins begin at the first date for which all candidate SDFs satisfy the
minimum effective-vintage and Jacobian conditions. At each origin, cash flows,
NAVs, factors, and state variables are truncated to their admissible information
date. Under Protocol~A no origin-level tuning occurs; under the sequential
Protocol~B, design selection at each origin uses strictly earlier origins
only. The final extract does not reconstruct
historical database coverage or later backfills; this pragmatic limitation is
disclosed and tested by excluding observations with suspiciously late first
reporting where such timestamps exist. The stronger literal real-time standard
would otherwise reduce the usable evaluation sample to essentially zero.

\subsection{Pre-Specified Design Grid}

The grid is intentionally coarse. Its final endpoints are fixed after a
descriptive feasibility audit, but before comparing out-of-sample losses.

\begin{table}[htbp]
\centering
\caption{Pre-specified empirical design}
\label{tab:design}
\small
\begin{tabular}{p{0.23\textwidth}p{0.29\textwidth}p{0.39\textwidth}}
\toprule
Object & Baseline candidates & Restriction or robustness \\
\midrule
SDF (benchmark $\beta$) & $\beta=0$; $\beta=1$ (PME); estimated $\beta$; multifactor $\beta$
    & Common factor set at every origin \\
Historical weighting & Expanding; rolling; exponential decay; time--state
    & Same candidate sequence for every SDF \\
Rolling length & 8, 12, 16 vintages
    & Retained only when identification is adequate \\
Time half-life & 4, 8, 12 vintage years
    & $h=\infty$ reproduces no decay \\
State bandwidth & 0.75, 1.5, 3 standardized units
    & $b=\infty$ reproduces time-only weighting \\
Young-fund treatment & Exclude; short-horizon NAV Euler hybrid
    & Common later realized-cash-flow target \\
Seasoning threshold & Residual value share at most 15\%
    & 10\%, 20\%, and zero residual value \\
Feasibility & $V_{\mathrm{eff}}\geq\max\{8,3\dim(\theta)\}$, incl.\ seasoned block
    & Jacobian conditioning reported separately \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Empirical Workflow}

The empirical analysis proceeds in the same order as the methodology:
\begin{enumerate}
\item construct seasoned realized-cash-flow moments and document calendar-time
      overlap across vintages;
\item estimate fully realized local SDFs and form the ex-post historical
      transportability matrix;
\item reconstruct pseudo-real-time origins and calculate feasible expanding,
      rolling, decaying, and time--state estimates;
\item select tuning parameters using earlier origins only;
\item score all candidates on the same later realized-cash-flow outcomes and
      compare exclusion with the short-horizon NAV Euler hybrid; and
\item re-estimate the selected specification at the final information date and
      report both its current SDF parameters and the historical weights that
      support them.
\end{enumerate}

\section{Empirical Results}

\subsection{The Effective Historical Sample}

Table~\ref{tab:sample} first documents the nominal and effective sample size.
A vintage-by-calendar-year cash-flow heat map shows the long overlap of fund
lives, while the overlap matrix $O$ summarizes common factor exposure. We
report the eigenvalue-based effective temporal rank and effective vintage
counts under each candidate weighting rule. This section establishes how much
independent economic history is actually available before asking whether old
history remains relevant.

\subsection{Ex-Post Historical Transportability}

The first main figure is the historical transportability matrix for the
baseline SDF. Rows identify estimation windows, columns identify excluded
realized vintages, and colors represent realized pricing loss. Signed-distance
loss curves then summarize forward and backward transport. The empirical
questions are whether loss rises with temporal distance, whether the pattern is
asymmetric, and whether particular evaluation vintages are difficult for every
historical window. Signed residuals are also plotted against realized
evaluation-window premia, implementing the premium-exposure diagnostic of
Section~\ref{sec:transportmeaning}.

\subsection{How Much History Travels Forward?}

The main model-comparison table reports paired forward loss for the expanding,
rolling, decay, and time--state estimators on common origin--vintage cells. For
each design we report average loss, the difference relative to expanding
history, origin-level uncertainty, $V_{\mathrm{eff}}$, and the fraction of
origins passing identification checks. This table supplies the paper's primary
answer: whether using less, or selectively weighted, history improves pricing
of later realized private-capital cash flows.

\subsection{Does Economic-State Similarity Add Information?}

We next hold the time-weighting rule fixed and compare time-only with time--state
weights. Weight plots show which distant vintages are recovered because their
credit spreads, interest rates, or public valuations resemble the target.
Leave-one-state-variable-out results reveal whether improvement is broad-based
or driven by a single state proxy. A state-conditioned estimator is preferred
only if it improves forward loss without collapsing the effective vintage
count.

\subsection{Do Unseasoned Vintages Improve the Current SDF?}

For every admissible origin, we compare the exclusion and short-horizon NAV
Euler estimators using identical later realized cash flows. The main table
reports paired loss differences overall and by the age of the young funds at
the estimation origin. We also relate the hybrid's gain to its NAV share and
subsequent NAV revisions. This distinguishes useful early information from a
mechanical fit to smoothed reported values.

\subsection{The Preferred SDF and the Pricing of Recent Vintages}

The final results section re-estimates the preferred design at the current
information date. We report the estimated benchmark exposures, the weights
assigned to every historical vintage, and the out-of-window pricing residuals
of recent vintages under the estimated law. In-window residuals are
shown only as fit diagnostics, since average in-window performance is
absorbed by construction. Sensitivity is reported across all configurations
in the model confidence set. The conventional expanding-history estimate is
shown alongside it so that the effect of historical transportability is
transparent.

\section{Robustness and Method Validation}

\subsection{Alternative Sample and Moment Choices}

Robustness exercises vary the seasoning threshold, exclude residual NAV
entirely, remove the financial-crisis and pandemic vintages one at a time,
alter fund-size reliability weights, and restrict the sample by strategy or
geography where coverage permits. Results are also reported with vintage-
equal weighting so that a few data-rich vintage years cannot determine the
conclusion.

\subsection{Alternative Windows, States, and SDFs}

We vary the coarse window grid, use a real rather than nominal long rate,
replace the valuation proxy, winsorize state distances, and compare the common
bandwidth with a strongly regularized variable-specific bandwidth. The smooth
time-varying parameter path is retained as a sophistication check. Alternative
SDFs matter only insofar as the transportability result survives reasonable
pricing specifications.

\subsection{Placebos}

Two placebos discipline the interpretation of state similarity. First, state
vectors are permuted across vintages while their time ordering is retained.
Second, the target state is replaced by a future state that was unavailable at
the origin. Genuine transport gains should disappear under the first placebo;
the second quantifies how much an inadvertently forward-looking state
construction could exaggerate performance.

\subsection{Compact Method Validation}

A standalone simulation section is not required for the paper's main empirical
claim. The estimator is selected by observed forward realized-cash-flow loss,
and a large menu of simulated breaks would not establish which process
generated the single historical private-capital sample. A compact appendix
calibration can nevertheless provide a useful diagnostic. It should match the
empirical vintage count, cash-flow-age profile, and calendar overlap under only
two designs --- a stable SDF and a smoothly drifting SDF --- each with and
without appraisal smoothing. Its limited purpose is to verify that the
selection procedure does not mechanically prefer short windows, state
conditioning, or the NAV bridge when the pricing law is stable. The empirical
transport and delayed-outcome exercises remain the evidence of interest.

\clearpage
\section{Conclusion}

Private-capital SDF estimation cannot solve a thin and delayed economic history
by resampling funds more aggressively. The relevant choice is which historical
vintages to transport to the target period and whether partial information from
recent funds improves that transport. The proposed estimator makes both choices
empirical: it weights history by time and observable economic similarity,
admits recent NAV information only through a short-horizon bridge, and selects
the complete design by its ability to price later realized cash flows. The
result is a current SDF supported by the part of history that has demonstrated
the greatest forward relevance, rather than by the longest history available.

\bibliographystyle{plainnat}
\bibliography{resampling_refs}

\end{document}
