\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}
\setlist[itemize]{leftmargin=1.3em,itemsep=0.2em,topsep=0.2em}

\begin{document}

{\Large\bfseries Resampling-Based Model Selection for PE SDFs\par}
{\normalsize How to empirically measure the risk-adjusted performance of PE\par}
\today

\section{Goal and Positioning}

Our goal is to develop a \emph{new resampling-based estimation method} that empirically determines which candidate SDF models are most credible for private-equity cash flows.

The central idea is simple. Suppose a candidate SDF model has \(p\) parameters. Then we can repeatedly partition the available vintage-year portfolios into \(p\) disjoint folds and use those \(p\) folds as \(p\) aggregated pricing moments in a KN16-style estimator. If the number of admissible partitions is too large, we sample from that partition set. The paper then asks whether the resulting exact-identified estimates are stable across partitions and, more importantly, whether they price \emph{held-out} vintage folds well.

This means the new paper is primarily a model-selection and empirical-design paper. It is closer in spirit to KN16 than to DLP12 because the estimation engine is built around aggregated pricing moments. DLP12 still matters because the choice of primitive pricing error and alpha parameterization remains central \citep{DriessenLinPhalippou2012,KortewegNagel2016}.

\section{Why Resampling Is Needed}

Private-equity samples are too small and too dependent to rely on one arbitrary partition of vintages into pricing moments. A single three-fold split for a three-parameter model can be highly unrepresentative. Resampling over many admissible partitions addresses this directly.

At the same time, exact-identified in-sample fit is not enough for comparing different candidate models (e.g. two-parameter models with different factors, or a two- versus a three-factor model). 
If a model with \(p\) parameters is estimated on exactly \(p\) aggregated folds, it can often fit those \(p\) moments very closely by construction. 
Therefore:

\begin{itemize}
\item \textbf{\(p\)-fold estimation} is useful for parameter recovery, feasibility, and stability diagnostics.
\item \textbf{\(p+1\)-fold estimation} is needed for genuine model ranking, because the extra fold creates an out-of-sample validation pricing moment.
\end{itemize}

So the paper should not drop cross-validation in substance. 
It should instead use a PE-specific form of repeated blocked sample splitting centered on holdout pricing error.
For better model selection, $p$ shall be selected as the maximum number of parameters among all candidate models.

\section{Primitive Units, Folds, and Admissible Partitions}

Let \(v=1,\dots,V\) index primitive vintage-year portfolios. For candidate model \(M\), let \(\theta\in\Theta_M\subset\mathbb{R}^{p(M)}\) denote the parameter vector. In sampled split \(n=1,\dots,N\), draw an admissible partition
\[
\mathcal P_n=\{F_{n,1},\dots,F_{n,p+h}\}
\]
of the vintage set into \(p+h\) disjoint folds, where \(p=p(M)\) and \(h\ge 0\) is the number of holdout folds.

The admissible partition set should enforce basic empirical discipline, for example:

\begin{itemize}
\item minimum number of underlying funds per fold,
\item minimum capital or NAV per fold,
\item no trivially tiny or empty folds,
\item reasonable balance across vintages.
\end{itemize}

If the number of admissible partitions is manageable, we can enumerate them. If it is too large, we sample Monte Carlo draws from that admissible set.

\section{Resampled KN16-Style Estimation}

\subsection{Fold pricing moments}

Let \(m_{n,j}(\theta;M,\eta)\) denote the pricing moment formed from fold \(F_{n,j}\) under candidate model \(M\) and design choice \(\eta\). The key point is that each fold contributes \emph{one aggregated pricing moment}, so the estimator is KN16-style at the level of aggregation logic.

For a three-parameter model, a sampled three-fold partition therefore gives three pricing moments:
\[
m_{n,1}(\theta)=0,\qquad
m_{n,2}(\theta)=0,\qquad
m_{n,3}(\theta)=0.
\]

\subsection{Exact-identified baseline: \(p\)-fold estimation}

When \(h=0\), each sampled partition contains exactly \(p\) folds. The split-specific estimate solves
\[
\hat\theta_n(M,\eta)
=
\arg\min_{\theta\in\Theta_M}
\frac{1}{p}\sum_{j=1}^{p}
L\!\left(m_{n,j}(\theta;M,\eta)\right).
\]

This is the natural baseline estimator because it uses the minimum number of aggregated moments needed for identification. Across many sampled partitions, it produces a distribution of split-specific estimates \(\hat\theta_n\). That distribution is already informative about:

\begin{itemize}
\item numerical feasibility,
\item parameter stability,
\item sensitivity to vintage partition choice,
\item boundary behavior and weak-identification problems.
\end{itemize}

But by itself it is not enough for model selection, because a just-identified model can often fit those \(p\) moments too easily.

\subsection{Holdout model selection: \(p+1\)-fold estimation}

The core model-selection design should therefore use \(h=1\). For each sampled partition, use \(p\) folds for estimation and one fold for holdout evaluation. Denote the estimation fold set by \(E_n\) and the holdout fold by \(H_n\). Then
\[
\hat\theta_n(M,\eta)
=
\arg\min_{\theta\in\Theta_M}
\frac{1}{p}\sum_{j\in E_n}
L\!\left(m_{n,j}(\theta;M,\eta)\right),
\]
and the holdout pricing score is
\[
S_n(M,\eta)
=
L\!\left(m_{n,H_n}(\hat\theta_n(M,\eta);M,\eta)\right).
\]

Aggregate across sampled partitions:
\[
\mathrm{Score}_N(M,\eta)
=
\frac{1}{N}\sum_{n=1}^{N} S_n(M,\eta).
\]

This is the key criterion for the new paper. The preferred SDF model is the one with the best average holdout pricing performance, not the one with the best in-sample exact-identified fit.

\subsection{Generalization}

The same framework naturally accommodates:

\begin{itemize}
\item \textbf{\(p\)-fold only:} exact-identified stability analysis,
\item \textbf{\(p+1\)-fold:} main model-selection design,
\item \textbf{\(p+2\)-fold estimation} with an additional partition which discards "too correlated" or not needed observations in the spirit of \cite{Racine2000},
\item \textbf{\(p+h\)-fold with \(h>1\):} richer holdout evaluation,
\item \textbf{\(p'>p\) estimation folds:} overidentified variants as robustness checks.
\end{itemize}

For the first version of the paper, the cleanest design is:

\begin{itemize}
\item main specification: \(p+1\),
\item robustness 1: \(p\),
\item robustness 2: \(p+2\) or \(p+1\) with alternative fold-balance constraints.
\end{itemize}

\section{Alpha Design}

Even though the estimation engine is KN16-style, the choice of primitive pricing moment remains open. This is where the DLP12 and KN16 traditions enter the new paper.

\subsection{Recommended baseline: cumulative alpha}

For fold \(F_{n,j}\), let the benchmark portfolio path implied by factor loadings \(\beta\) be \(B_t(\beta)\). The exact direct-alpha-style fold moment is
\[
\psi_{n,j}(a,\beta)
=
\sum_t \frac{cf_{n,j,t}}{B_t(\beta)}
\exp\!\left(-a\,\tau_{n,j,t}\right),
\]
where \(\tau_{n,j,t}\) is elapsed time from the fold origin to date \(t\). Equivalently, for fixed \(\beta\), the fold-implied cumulative alpha \(a_{n,j}(\beta)\) solves
\[
\sum_t \frac{cf_{n,j,t}}{B_t(\beta)}
\exp\!\left(-a_{n,j}(\beta)\,\tau_{n,j,t}\right)=0.
\]

This should be the recommended baseline because:

\begin{itemize}
\item it keeps alpha cumulative rather than period-by-period,
\item it is much closer to KN16 / GPME / direct-alpha logic,
\item it avoids the worst exploding-alpha geometry of monthly intercept-alpha estimation,
\item it yields a natural abnormal-performance object that can be annualized only after estimation \citep{KortewegNagel2016,GredilGriffithsStucke2023,KortewegNagel2025}.
\end{itemize}

\subsection{Alpha as mean of the error-term series}

Using the machine-learning approach of \cite{TauschPietz2024}.
Alpha is then the mean value of the error time series $\alpha=\mathbb{E}[\epsilon]$.

\subsection{Intercept alpha as a robustness design}

If the paper still wants to include a DLP12-style intercept alpha, it should be treated as a robustness design rather than as the main estimator. In that case the pricing moments should be built from a transformed objective, such as log-ratio or PME-style moments, not from the raw NPV criterion \citep{DriessenLinPhalippou2008WP}. A penalty on the alpha direction can also be justified when the split-specific exact-identified solutions are numerically unstable \citep{StockWright2000,CuiFengHong2024}.

\section{Relation to DLP12 and KN16}

The paper should present the new method as follows.

\begin{itemize}
\item \textbf{KN16 contribution retained:} the estimator uses aggregated pricing moments and is naturally expressed through repeated grouped partitions of the data.
\item \textbf{DLP12 contribution retained:} the moments still price private cash flows directly, and the primitive pricing restriction can be DLP12-like if desired.
\item \textbf{New contribution:} instead of committing to one partition, the paper resamples many admissible partitions and ranks candidate models by holdout pricing performance.
\end{itemize}

So the main innovation is not ``fixing'' the old SDF paper. It is turning partition choice itself into an empirical object.

\section{Practical Algorithm}

For each candidate model \(M\):

\begin{itemize}
\item Determine \(p=p(M)\).
\item Construct the admissible set of disjoint \((p+h)\)-fold partitions of vintage-year portfolios.
\item Enumerate all such partitions if feasible; otherwise sample \(N\) partitions from that set.
\item For each partition \(n\), estimate \(\hat\theta_n(M,\eta)\) on the \(p\) estimation folds.
\item Score \(\hat\theta_n(M,\eta)\) on the \(h\) holdout folds.
\item Aggregate holdout losses across \(n\).
\item Rank candidate models by average holdout pricing loss.
\end{itemize}

Alongside the mean holdout loss, report:

\begin{itemize}
\item median holdout loss,
\item dispersion of \(\hat\theta_n\),
\item frequency of non-convergence,
\item frequency of boundary solutions,
\item conditioning or curvature diagnostics.
\end{itemize}


\bibliographystyle{plainnat}
\bibliography{resampling_refs}

\end{document}
